\chapter{Visual Exploration of Human-Scale Urban Forms Based on Street Views}\label{chap:intro}
\QM{Urban forms at human-scale, i.e., urban environments that individuals can sense (e.g., sight, smell, and touch) in their daily lives, can provide unprecedented insights on a variety of applications, such as urban planning and environment auditing.
The analysis of urban forms can help planners develop high-quality urban spaces through evidence-based design.
However, such analysis is complex because of the involvement of spatial, multi-scale (i.e., city, region, and street), and multivariate (e.g., greenery and sky ratios) natures of urban forms.
In addition, current methods either lack quantitative measurements or are limited to a small area. 
The primary contribution of this work is the design of StreetVizor, an interactive visual analytics system that helps planners leverage their domain knowledge in exploring human-scale urban forms based on street view images.
Our system presents two-stage visual exploration: 
1) an AOI Explorer for the visual comparison of spatial distributions and quantitative measurements in two areas-of-interest (AOIs) at city- and region-scales;
2) and a Street Explorer with a novel parallel coordinate plot for the exploration of the fine-grained details of the urban forms at the street-scale.
We integrate visualization techniques with machine learning models to facilitate the detection of street view patterns. 
We illustrate the applicability of our approach with case studies on the real-world datasets of four cities, i.e., Hong Kong, Singapore, Greater London and New York City.
Interviews with domain experts demonstrate the effectiveness of our system in facilitating various analytical tasks.}

\input{chapter/2_StreetVizor/1_Introduction.tex}

\input{chapter/2_StreetVizor/2_relatedwork.tex}

\input{chapter/2_StreetVizor/3_BackgroundAndTask.tex}