\acknowledgments
First, I   want to express my gratitude to my supervisor and mentor, Prof. Huamin Qu, who strongly supported my research, career, and personal endeavors. I enjoyed the short discussions with Prof. Qu, which were beneficial during my moments of difficulty. His guidance and support enabled me to fully understand research and my capabilities. In particular, he provided me with numerous opportunities to collaborate with renowned researchers, thereby expanding my horizon in this undertaking. To date, I consider myself fortunate to have had the opportunity to send him my first e-mail expressing my intention to visit VisLab in 2014, when his team was smaller than its current composition. In the succeeding five years, I have witnessed the growth and success of our group. I am deeply appreciate that Prof. Qu bring me to fantastic group. I am really proud to be a member in this big family. 

I am likewise extending my gratitude to all my highly capable academic colleagues. This thesis would not have been completed without their valuable assistance. 
I want to specifically thank Dr. Wei Zeng for our extensive collaboration in my research projects. Apart from being a reliable research partner and best friend, he has taught me substantially invaluable lessons on presentation and writing. 
I am also expressing my sincere appreciation of Prof. Anna Vilanova for providing me with the opportunity to visit Delft University of Technology and collaborate with my research topics. She is definitely a good, enthusiastic, and patient friend and teacher. 
I am likewise grateful to Yong Wang, Yanhong Wu, Tongshuang Wu, Qianwen Wang, Yuzhe Jiang, Yu Ye, Yao Ming, Quan Li, Weiwei Cui, and Dr. Bing Ni for their considerable assistance in my research. I am honored that I was able to work with and learn from them. 

Studying in the Hong Kong University of Science and Technology is a turning point in my life, and I am fortunate to have met and became friends with many notable and capable people. 
The past five years have been replete with joy, and I would like to reiterate my appreciation of Yong Wang, Yanhong Wu, Haipeng Zeng, Quan Li, Conglei Shi, Qing Chen, Panpan Xu, Dongyu Liu, Zhutian Chen, Wenbin Wu, Siwei Fu, Yun Wang, Yuanzhe Chen, Qianwen Wang ,Ke Xu, Yeuk Yin CHAN, Zhida Sun, and Mingfei Sun, the old guys from Room 2394, they help me a lot in my early tough studies. I would also want to thank Yao Ming, Xuanwu Yue, Wenchao Li, Dong Sun, Xinhuan Shu, Meng Xia, Yifang Wang, Furui Cheng, Leni Yang, Renfei Huang, Yuzhe Jiang, Xingbo Wang, Zezheng Feng, Auyu Wu, Zhihua Jin, Linping Yuan, and Hua Wei. After I transferred to Office CYT3007, these new generation of individuals impressed me with their talent, creativity, and optimism, thereby enabling me to learn substantially from them. 

Moreover, I would like to thank the thesis examination committee members: Prof. Raymond Wong, Prof. Wilfred Ng, Prof. Hai Yang, Prof. Man Sun Chan, and Prof. Xiaoru Yuan. Special mention goes to Prof. Yuan, who instituted the renowned visualization summer school in Peiking University, where I met my supervisor for the first time.  

I am also grateful to all my old friends who have consistently assisted and encouraged me in my academic endeavors for the past 20 years. Bo Tang and Li Xiao from Shenzhen particularly provided me with free housing, BBQ, workstation, and other crucial assistance. I am also expressing my appreciation of my real friends, namely, Li Ma, Qing Ye, Xi, Nie, Li Lv, Chunhong Chen, Shouning Yuan, Renji Liu, and Haoran Jing.

My most special gratitude goes to my family. My parents and parents-in-law have provided me with their endless support and love, thereby encouraging me to face any difficulties as I complete my thesis. I am likewise expressing my sincerest gratitude to my beloved soulmate, Dan Zeng, who experienced six years of long-distance love with me. She is a postdoc who also faces the same challenges that I constantly encounter, although she is more patient and understanding than I am in times of difficulty. During the lowest moment in my life, she told me that “whatever happens, I’ll always be on your side.” My family is truly my source of inspiration to overcome the obstacles that I encounter in life.

Once again, I thank everyone who have accompanied me through this crucial and memorable period in my life.


\endacknowledgments
