\chapter{Route-Aware Edge Bundling for Visualizing Origin-Destination Trails in Urban Traffic}\label{chap:c2_intro}

Origin-destination(OD) trails describe movements across geographical locations, which can be visualized as direct lines connecting ODs.
The visualization method, however, causes clutter issues for large amounts of OD trails.
Edge bundling methods can mitigate the problem, yet bundling OD trails in urban traffic data remains under-explored.
This work presents a new approach, namely route aware edge bundling (RAEB), specifically designed to fill the gap.
We identify inconsiderate settings of conventional kernel density estimation edge bundling (KDEEB) when applied to urban traffic data, including non-optimal kernel size and road neglect.
The limitations are addressed in RAEB by introduction of a comprehensive pipeline comprising preprocessing, bundling and evaluation processes.
A series of new parameters, together with adaptions of existing ones, are employed in the pipeline.
Experiments with artificial and real-world traffic data demonstrate advancements of RAEB in various applications, including preservation of road network topology and support of multi-scale exploration.


\input{chapter/3_edgebundling/1_Introduction.tex}
\input{chapter/3_edgebundling/2_relatedwork.tex}
\input{chapter/3_edgebundling/3_Overview.tex}

\input{chapter/3_edgebundling/4_InputAndPreprocessing.tex}
\input{chapter/3_edgebundling/5_EdgeBundling.tex}

\input{chapter/3_edgebundling/6_Evaluation.tex}
\input{chapter/3_edgebundling/7_ExperimentalResults.tex}
\input{chapter/3_edgebundling/8_Discussion.tex}
\input{chapter/3_edgebundling/9_Conclusion.tex}
